Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-10-13 ms.tex
show the trends with time for the multiple exposures.

\subsection{Long multi-exposure Test}
\textbf{\textcolor{red}{Show exposure boundaries}}

\begin{figure*}
{\gridline{\fig{individual_azlab06_sub320_multi_exp.pdf}{0.48\textwidth}{AZLab06 Long Multi-Exposure Time series}
\fig{all_var_azlab06_sub320_multi_exp_487_489_removelinear_True_489.pdf}{0.48\textwidth}{AZLab06 Allan variance for Multi-exp Series}}}
\caption{We strung together 4 long exposures to create an extended time series.
There are no obvious transients or exponentials at the exposure boundaries, which are marked as vertical blue lines.
As with previous tests, the standard deviation is well above the photon and read noise value and furthermore doesn't scale with the $\sqrt{N}$ for $N$ points in a bin.
}\label{fig:AZlab06LongMultiExp}
\end{figure*}

>>>>

\subsection{Long multi-exposure Test}
A long multi-exposure time series shows the noise properties on timescales up to a few hours.
This long series also enables a clearer trending with temperature and flux.

\begin{figure*}
{\gridline{\fig{individual_azlab06_sub320_multi_exp.pdf}{0.48\textwidth}{AZLab06 Long Multi-Exposure Time series}
\fig{all_var_azlab06_sub320_multi_exp_487_489_removelinear_True_489.pdf}{0.48\textwidth}{AZLab06 Allan variance for Multi-exp Series}}}
\fig{individual_azlab06_sub320_multi_exp_w_time}{0.48\textwidth}{Multi-Exposure Time series with temperature data}
\caption{We strung together 4 long exposures to create an extended time series.
There are no obvious transients or exponentials at the exposure boundaries, which are marked as vertical blue lines.
As with previous tests, the standard deviation is well above the photon and read noise value and furthermore doesn't scale with the $\sqrt{N}$ for $N$ points in a bin.
}\label{fig:AZlab06LongMultiExp}
\end{figure*}
